Supplementary Material

### 2019-06-14 supplement.tex
Add supplementary material

We also tried replacing the ReLU activations with SELUs \cite{klambauer_self-normalizing_2017} but saw little if any improvement and therefore returned to using ReLUs.

@@

Autoencoder

Discriminator

Datasets

@@

\subsubsection{Data Format}

@@

GSE37199

@@

Other methods

We wanted to also compare with SVA \cite{leek_capturing_2007} and the Shaham lab's work \cite{shaham_removal_2017,shaham_batch_2018} but were unable to get these two methods to work.
With SVA, the documentation showed how to identify surrogate variables and use them in modeling, but we were unable to find examples of removing the effects that those surrogate variables represent.
We were unable to get the Shaham lab's methods running on our datasets, and we believe that this is due to some underlying assumptions in their code (see \ref{section:mmd} for more information).

MSE

@@

MMD

@@

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{setspace}
% \usepackage{authblk}
\usepackage{url}
\usepackage[inline,shortlabels]{enumitem}
\usepackage[square,numbers]{natbib}
\usepackage{floatrow}
\floatsetup[table]{capposition=top}
\usepackage[nomarkers,nolists]{endfloat}
\usepackage[margin=1in,letterpaper]{geometry}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{lineno}
\linenumbers

\bibliographystyle{unsrtnat}

\begin{document}

\title{Supplementary Material}
\date{\vspace{-5ex}}

\maketitle

\doublespacing

\section{Optimizing default parameters}

We tried a number of parameter optimizations to set reasonable defaults.
We list them below and further discuss the bolded items.

\paragraph{Things that helped}

\begin{enumerate}
	\item \textbf{Adjust autoencoder depth}
	\item \textbf{Adjust discriminator depth}
	\item \textbf{Scale to [0, 1] with sigmoid}
	\item Make code layer more narrow
	\item Optimizing cross-entropy instead of MSE - trains faster
	\item Adjusting the lambda value - somewhat dataset specific
	\item Variational instead of normal autoencoder - loss is less erratic
	\item Dropout in the discriminator - less overfitting
\end{enumerate}

\paragraph{Things that didn't help}

\begin{enumerate}
	\item ReLU vs SELU \cite{klambauer_self-normalizing_2017} activation - no difference
	\item Recurrent discriminator connections - no difference
	\item Recurrent autoencoder connections (like UNet) - no difference
	\item Training autoencoder, discriminator, then dual optimizers sequentially - did worse
	\item Stopping early - did worse
\end{enumerate}

\paragraph{Adjust autoencoder depth}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/supplement/ae_layers.png}
	\caption{\textbf{Loss vs. Number of Autoencoder Layers}
	}
	\label{fig:ae}
\end{figure}

\paragraph{Adjust discriminator depth}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/supplement/disc_layers.png}
	\caption{\textbf{Loss vs. Number of Discriminator Layers}
	}
	\label{fig:disc}
\end{figure}

\paragraph{Scale to [0, 1] with sigmoid}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/supplement/scaling.png}
	\caption{\textbf{Loss vs. Scaling Method}
	}
	\label{fig:scaling}
\end{figure}

\paragraph{Other ideas}

@@

\paragraph{Datasets}

@@

\section{Data Format}

@@

\paragraph{GSE37199}

@@

\section{Testing different-sized datasets}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/supplement/tcga_mse.pdf}
	\caption{\textbf{TCGA MSE}
	}
	\label{fig:mse}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/supplement/tcga_mmd.pdf}
	\caption{\textbf{TCGA MMD}
	}
	\label{fig:mmd}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/supplement/tcga_true_class_accuracy.pdf}
	\caption{\textbf{TCGA True Class Accuracy}
	}
	\label{fig:true_class}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/supplement/tcga_batch_accuracy.pdf}
	\caption{\textbf{TCGA Batch Accuracy}
	}
	\label{fig:batch}
\end{figure}

\section{Other methods}

We wanted to also compare with SVA \cite{leek_capturing_2007} and the Shaham lab's work \cite{shaham_removal_2017,shaham_batch_2018} but were unable to get these two methods to work.
With SVA, the documentation showed how to identify surrogate variables and use them in modeling, but we were unable to find examples of removing the effects that those surrogate variables represent.
We were unable to get the Shaham lab's methods running on our datasets, and we believe that this is due to some underlying assumptions in their code.

\section{Metrics used}

\paragraph{MSE}

@@

\paragraph{MMD}

@@

\paragraph{PCA \& t-SNE}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/supplement/mnist_pca.pdf}
	\caption{\textbf{MNIST PCA}
	}
	\label{fig:pca}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/supplement/mnist_tsne.pdf}
	\caption{\textbf{MNIST t-SNE}
	}
	\label{fig:tsne}
\end{figure}

\bibliography{references}

\end{document}
